\documentclass[12pt]{my_cv}
\usepackage[margin=3cm]{geometry}
\usepackage{array}
\newcolumntype{L}{p{0.2\textwidth}}
\newcolumntype{R}{p{0.74\textwidth}}
\def\ind{\hangindent=1 true cm\hangafter=1 \noindent}

\begin{document}

\noindent \textbf{\sffamily\Large Alexander S. Rich}\vspace{1em}\\
Department of Psychology\\
New York University\\
6 Washington Place\\
 New York, NY 10003\\
email: asr443@nyu.edu\\

\section{Education}
\begin{tabular}{L R}
2013--present&New York University\\
&Psychology: Cognition and Perception with Quantitative Minor\\
&Ph.D. expected 2018\\
&Advisor: Dr.\ Todd Gureckis \vspace{1em}\\ 
2009--2013&Williams College\\
&B.A. Mathematics, \emph{Magna Cum Laude}, Phi Beta Kappa\\
&Concentration with Honors in Cognitive Science\\
&Advisor: Dr.\ Safa Zaki\\
\end{tabular}

\section{Honors and Fellowships}
\begin{tabular}{L R}
2015, 2014&Robert J. Glushko and Pamela Samuelson Foundation Student Travel Grant for attendance at the annual meeting of the Cognitive Science Society\\[1ex]
2015&Honorable Mention, National Science Foundation Graduate Research Fellowship\\[1ex]
2013--2018&MacCracken Fellowship, New York University\\
\end{tabular}

\section{Peer Reviewed Journal Articles}

\ind \textbf{Rich, A.S.}, Gureckis, T.M. (2017). Exploratory choice
reflects the future value of information. \emph{Decision}.

\ind Gureckis, T.M., Martin, J., McDonnell, J., \textbf{Rich, A.S.}, Markant,
D., Coenen, A., Halpern, D., Hamrick, J.B., Chan, P. (2015). psiTurk: an
open-source framework for conducting replicable behavioral experiments online.
\emph{Behavior Research Methods}.

\section{Manuscripts}

\ind \textbf{Rich, A.S.}, Gureckis, T.M. \emph{in review}. The limits of learning:
Exploration, generalization, and the development of learning traps.

\ind \textbf{Rich, A.S.}, Gureckis, T.M. \emph{in preparation}. Effects of
present bias on exploratory choice. (Preregistration: osf.io/2pvx8)

\section{Refereed Conference Proceedings}

\ind \textbf{Rich, A.S.} Popp, P.J., Halpern, D., Rothe, A. and Gureckis, T.M.
(2018). ``Modeling Second-Language Learning from a Psychological Perspective''
in \emph{Proceedings of the NAACL-HLT Workshop on Innovative Use of NLP for
  Building Educational Applications (BEA).} Association for Computational Linguistics.	

\ind Rothe, A., \textbf{Rich, A.S.} and Li, Z. (2018). ``Topics and Trends in Cognitive Science'' in \emph{Proceedings of the 40th Annual Conference of the Cognitive Science Society.} Cognitive Science Society.	

\ind \textbf{Rich, A.S.} and Gureckis, T.M. (2015). ``The Attentional Learning Trap and How to Avoid It'' in \emph{Proceedings of the 37th Annual Conference of the Cognitive Science Society.}  Cognitive Science Society.	

\ind \textbf{Rich, A.S.} and Gureckis, T.M. (2014). ``The value of approaching bad things'' in \emph{Proceedings of the 36th Annual Conference of the Cognitive Science Society.} Cognitive Science Society.	

\section{Professional Presentations}

\ind Gureckis, T.M. and \textbf{Rich, A.S.} (June 2017). ``Creating online
experiments with psiTurk'' Data on the Mind Workshop, Berkeley, CA, USA.

\ind \textbf{Rich, A.S.} and Gureckis, T.M. (August 2016). ``Exploratory choice
reflects the future value of information'' Talk presented at the International
Conference on Thinking, Providence, Rhode Island, USA.

\ind \textbf{Rich, A.S.} and Gureckis, T.M. (August 2015). ``The Attentional
Learning Trap and How to Avoid It'' Talk presented at the $37^{th}$ Annual Meeting of the
Cognitive Science Society, Pasadena, USA.

\ind \textbf{Rich, A.S.} and Gureckis, T.M. (August 2014). ``The value of
approaching bad things'' Talk presented at the $36^{th}$ Annual Meeting of the
Cognitive Science Society, Quebec City, Canada.

\ind de Leeuw, J.R., Coenen, A., Markant, D., Martin, J.B., McDonnell, J.V.,
\textbf{Rich, A.S.}, Gureckis, T.M. (2014). ``Workshop: Online Experiments Using
jsPsych, psiTurk, and Amazon Mechanical Turk'' in  Proceedings of the 36th Annual Conference of
the Cognitive Science Society. Cognitive Science Society.

\section{Poster Presentations}

\textbf{Rich, A.S.}, and Gureckis, T.M. (November 2017).
``Exploration, Generalization, and the Development of Learning Traps''
presented at the Annual Meeting of the Psychonomic Society, Vancouver, BC, Canada.

\ind \textbf{Rich, A.S.}, and Gureckis, T.M. (July 2017). ``Does a present bias
influence exploratory choice?'' presented at the 39th Annual Conference of
the Cognitive Science Society, London, UK.

\ind Zaki, S., \textbf{Rich, A.}, and Stacy, S. (November 2016).
``Temporal juxtaposition in category learning: modeling and eye tracking data.''
 presented at the Annual Meeting of the Psychonomic Society, Boston, MA, USA.

\ind \textbf{Rich, A.S.}, and Gureckis, T.M. (November 2015). ``The attentional
learning trap: How selective attention can cause persistent false beliefs''
presented at the Annual Meeting of the Society for Judgment and Decision
Making, Chicago, IL, USA.

\ind Gureckis, T.M., and \textbf{Rich, A.S.} (November 2015). ``Approach-avoid
decisions reflect the value of information'' presented at the Annual
Meeting of the Society for Judgment and Decision Making, Chicago, IL, USA.

\ind Markant, D., Chan, P., Coenen, A., Martin, J., McDonnell, J., \textbf{Rich,
  A.} and Gureckis, T. M. (November 2014). ``psiTurk: An open-source framework
for conducting reproducible behavioral experiments online.'' presented at
the 2014 meeting of the Society for Computers in Psychology, Long Beach, CA,
USA.

\section{Research Experience}
\begin{tabular}{L R}
2013--present& Graduate Research Assistant\\
&Advisor: Dr.\ Todd Gureckis, New York University\\[1ex]
2012--2013& Research Fellow\\
&Advisor: Dr.\ Safa Zaki, Williams College\\[1ex]
2011&Research Assistant\\
&PI: Dr.\ Frank Keil, Yale University\\
\end{tabular}

\section{Professional Service}

Ad-hoc journal reviewing: \emph{Cognitive Science; Journal of Experimental
  Psychology: General; Cognitive, Affective, \& Behavioral Neuroscience;
  Annual Meeting of the Cognitive Science Society}

\section{Teaching}
\begin{tabular}{L R}
Spring 2018 & Teaching Assistant, \emph{Computational Cognitive Modeling} (graduate, NYU)\\ [0.5ex]
Fall 2015 & Teaching Assistant, \emph{Laboratory in Human Cognition} (undergraduate, NYU)\\ [0.5ex]
Fall 2014&Teaching Assistant, \emph{Mathematical Tools for Neural and Cognitive Science} (graduate, NYU)\\ [0.5ex]
Spring 2013&Teaching Assistant, \emph{Data Structures and Advanced Programming} (undergraduate, Williams)\\[0.5ex]
Fall 2012&Teaching Assistant, \emph{Introduction to Computer Science} (undergraduate, Williams)\\[0.5ex]
Spring 2012&Teaching Assistant, \emph{Linear Algebra} (undergraduate, Williams)\\[0.5ex]
Fall 2010&Teaching Assistant, \emph{Calculus II} (undergraduate, Williams)\\[0.5ex]
\end{tabular}

\end{document}